The illusory promise of the Aligned Rank Transform

### 2025-07-08 text/30-assumptions.qmd
correct figure 7

logm1 <- meanlog(0.8, 1)
logm2 <- meanlog(1.4, 1)

logsd1 <- sdlog(0.8, 1)
logsd2 <- sdlog(1.4, 1)

@@

annot1 <- paste("Log-normal: meanlog = ", round(logm1, 2), ", sdlog = ", round(logsd1, 2))
annot2 <- paste("Log-normal: meanlog = ", round(logm2, 2), ", sdlog = ",  round(logsd1, 2))

>>>>

sd <- 1 # This is the common standard deviation
m1 <- 0.8
m2 <- 1.4

logm1 <- meanlog(m1, sd)
logm2 <- meanlog(m2, sd)

logsd1 <- sdlog(m1, sd)
logsd2 <- sdlog(m2, sd)

@@

annot1 <- paste("Log-normal: mean = ", m1, ", sd = ", sd)
annot2 <- paste("Log-normal: mean = ", m2, ", sd = ", sd)
